\thesistitle

### 2019-07-29 sections/clonerefactor.tex
Class level clones

\begin{equation}\label{eq:sameclass}
\forall (n \in I)\text{ } Tn = \text{ MethodDeclaration } \lor \exists (p \in ancestors(n)) \text{ } Tp = \text{ MethodDeclaration }
\end{equation}

@@

\subsubsection{Class Level Clones}

\subsection{Contents}\label{sec:setupcontents}
Finally, we looked at what nodes individual clone instances span. We selected the following categories to be relevant for refactoring:
\begin{enumerate}
  \item \textbf{Full Method/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
  \item \textbf{Partial Method/Constructor:} A clone that spans a method partially, optionally including its declaration.
  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods (so not fields or anything in between).
  \item \textbf{Only Fields:} A clone that spans only global variables.
  \item \textbf{Includes Fields/Constructor:} A clone that spans a combination of fields and other things, like methods.
  \item \textbf{Method/Class/Interface/Enumeration Declaration:} A clone that contains the declaration (usually the first line) of a class, method, interface or enumeration.
  \item \textbf{Other:} Anything that does not match with above-stated categories.
\end{enumerate}

>>>>

\begin{equation}\label{eq:sameclass}
\forall (n \in I)\text{ } Tn = \text{MethodDeclaration} \lor \exists (p \in ancestors(n)) \text{ } Tp = \text{MethodDeclaration}
\end{equation}

@@

\subsubsection{Class/Interface/Enumeration Level Clones}
Class/Interface/Enumeration Level clone instances are found inside the body of one of these declarations and optionally include the declaration itself. It can also be a clone instance that exceeds the boundaries of a single method. These clone instances can contain a fields, (abstract) methods, inner classes, enumeration fields, etc. These types of clones require various refactoring techniques to refactor. For instance, we might have to move fields in a inheritance hierarchy. Or, we might have to perform a refactoring on more of an architectural level, if a large set of methods is cloned.

We detect these clones in the same way we detect method level clones: we walk up the AST until we find the first node that indicates one of these categories.

\subsection{Contents}\label{sec:setupcontents}
Finally, we looked at what nodes individual clone instances span. We selected the following categories to be relevant for refactoring:
\begin{enumerate}
  \item \textbf{Full Method/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
  \item \textbf{Partial Method/Constructor:} A clone that spans (a part of) the body of a method. The declaration itself is not included.
  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods (so not fields or anything in between).
  \item \textbf{Only Fields:} A clone that spans only global variables.
  \item \textbf{Includes Fields/Constructor:} A clone that spans a combination of fields and other things, like methods.
  \item \textbf{Method/Class/Interface/Enumeration Declaration:} A clone that contains the declaration (usually the first line) of a class, method, interface or enumeration.
  \item \textbf{Other:} Anything that does not match with above-stated categories.
\end{enumerate}
